Sr: Processing Data Streams and Avoiding Work

### 2012-05-04 paper/paper.tex
Formatting the hash code
more citations

\section{Introduction}
\label{sec:intro}
One of the fundamental problems MapReduce was created to solve was processing
the growing amount of data in the world. Now with the open source Apache Hadoop
and Pig~\cite{piglatin}, it is easy to process and query the terabytes of data an organization
may collect. With terabytes of data, however, it is scarcely necessary to examine
every entry to uncover trends. Google runs PageRank on the entire Internet, but if
it only did on half of the pages it crawls, it would likely still have a usable
index for delivering the first 5 pages of results.

How does one decide which data to process then? Selctively deciding which data to
log is problematic because it can systemically mask some of the trends one would
try to uncover through analysis. In this paper, I explore the possibility of
discarding data randomly and choosing to process the data I do see at differing
fidelities in order to save work.

@@

@@

The master is the only well-known node in the cluster. Other nodes in the network exclusively
communicate with the master. The master and other nodes communicate with each other by issuing
HTTP requests to a simple server on each node. I decided to make use of a library [Sinatra.rb]
providing the server functionality because there was a low barrier to getting inter-node
communication functioning. This design choice presents some problems and will be discussed
further in Section~\ref{sec:discussion}.

@@

Sr sends the source of the Jobfile to every node participating in the job and uses eval to
obtain a local instance of the Jobfile class. An example jobfile can be found at [github].

@@

\section{Methodology}
\label{sec:methodology}
The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers,
1 collector, and 1 master. Roles are partitioned among nodes as shown in
Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM [SIPB] VMs provisioned with 128MB RAM each.
The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.

@@

To run the job, I had to create a spout and find a source of data. For data, I acquired a
Wikipedia dump of the Featured Articles category. I used Wikipedia’s xml exporter
[Special:export] on January 9, 2012.

To serve the data, I munged it into a YAML file containing a hash of
\lstinline[language=Ruby]{article_id : fulltext}. To store fulltext, I base64 encoded it and
deflated it using zlib. This requires workers to inflate and decode the fulltext before they
can process it further. The server reads from this YAML file and returns the resulting hash as
JSON.

>>>>

\section{Introduction}
\label{sec:intro}
One of the fundamental problems MapReduce was created to solve was processing
the growing amount of data in the world. Now with the open source Apache Hadoop
and Pig~\cite{piglatin}, it is easy to process and query the terabytes of data an organization
may collect. With terabytes of data, however, it is scarcely necessary to examine
every entry to uncover trends, especially when one only cares about the most prominent
trends or results. Google runs PageRank on the entire Internet, but if
it only did on half of the pages it crawls, it would likely still have a usable
index for delivering the first 5 pages of results.

How does one decide which data to process then? Selctively deciding which data to
log is problematic because it can systemically mask some of the trends one would
try to uncover through analysis. In this paper, I explore the possibility of
discarding data randomly. On the subset of data that I do process, I explore using
computation routines of differing fidelities to sample the data. Combining both of these
techniques allows the cluster to avoid performing work.

@@

The goal of Sr is to be a MapReduce-style framework for processing streams. Such a
framework should include the ability to kill or discard tasks and provide serveral
different computation routines for workers to choose among.

@@

The master is the only well-known node in the cluster. Other nodes in the network exclusively
communicate with the master. The master and other nodes communicate with each other by issuing
HTTP requests to a simple server on each node. I decided to make use of a library~\cite{sinatrarb}
providing the server functionality because there was a low barrier to getting inter-node
communication functioning. This design choice presents some problems and will be discussed
further in Section~\ref{sec:discussion}.

@@

Sr sends the source of the Jobfile to every node participating in the job and uses eval to
obtain a local instance of the Jobfile class. An example jobfile can be found at~\cite{github}.

@@

\section{Methodology}
\label{sec:methodology}
The cluster I used to test Sr is a 5-node network consisting of 1 spout, 1 fetcher, 4 workers,
1 collector, and 1 master. Roles are partitioned among nodes as shown in
Figure~\ref{fig:clusterDiagram}. Worker nodes were XVM~\cite{sipb:xvm} VMs provisioned with 128MB RAM each.
The master, spout, fetcher, and collector ran on my laptop, a mid-2010 Macbook Air with 4GB of RAM.

@@

To run the job, I had to create a spout and find a source of data. For data, I acquired a
Wikipedia dump of the Featured Articles category. I used Wikipedia’s xml
exporter~\cite{wikipedia:pecial:export} on January 9, 2012.

To serve the data, I munged it into a YAML file containing a hash of
\begin{center}
$\texttt{article\_id}\rightarrow\texttt{fulltext}$.
\end{center}
To store fulltext, I base64 encoded it and
deflated it using zlib. This requires workers to inflate and decode the fulltext before they
can process it further. The server reads from this YAML file and returns the resulting hash as
JSON.
